Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-04 thesis/paper.tex
fixed a typo

The changes have been divided up into four specific categories, namely: new, modified, removed and general trends. New and modified changes concern additions of or modifications to modules and removed changes is functionality which have been removed entirely without being deprecating or replaced by new implementations. General trends are broad changes which do not directly affect functionality.

@@

\section{Discussion}
Our results have been provided valuable insight to the motives behind the evolution of an API. The results show that APIs definitely can be studied from the point of view of old evolution theories. Based on the result, we have formulated the subsequent outcomes.

>>>>

The changes have been divided up into four specific categories, namely: new, modified, removed and general trends. New and modified changes concern additions of or modifications to modules. Removed changes are functionality which have been removed entirely without being deprecated or replaced by new implementations. General trends are broad changes which do not directly affect functionality.

@@

\section{Discussion}
Our results have provided valuable insight to the motives behind the evolution of an API. The results show that APIs definitely can be studied from the point of view of old evolution theories. Based on the result, we have formulated the subsequent outcomes.
